Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Shrink system diagram
Shrink to 15 pages

\subsection{System Overview}
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{fig/system_diagram.eps}
	\caption{An architecture diagram showing the interactions within the system.}
	\label{fig:system_diagram}
\end{figure}

@@

\begin{figure}
	\centering
\includegraphics[width=\textwidth]{fig/Armadillo.png}
\caption{Screenshot of the Armadillo web application.}
\label{fig:armadillo}
\end{figure}

As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on \emph{BPMN Service Tasks}, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.

@@

In this paper, we presented a system architecture and prototypical implementation for connecting process execution with blockchain technology.
While keeping the process execution off-chain, we developed an approach of inter-process communication using the Ethereum blockchain as a messaging channel.
Having a permanent ledger as the underlying data structure storing messages, faults and misunderstandings can be traced back to their origin and responsibilities are disclosed.

Building on the findings of this paper, improvements regarding runtime and execution costs open up a wide area of possible future work on the topic.

>>>>

\subsection{System Overview}
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{fig/system_diagram.pdf}
	\caption{An architecture diagram showing the interactions within the system.}
	\label{fig:system_diagram}
\end{figure}

@@

\begin{figure}
	\centering
\includegraphics[width=0.8\textwidth]{fig/Armadillo.png}
\caption{Screenshot of the Armadillo web application.}
\label{fig:armadillo}
\end{figure}

As a way of joining process execution with our blockchain architecture, we developed a single page web application (see Figure \ref{fig:armadillo}) in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on BPMN \emph{Service Tasks}, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/Armadillo/blob/master/armadillo-screencast.mp4}.

@@

In this paper, we presented a system architecture and prototypical implementation for connecting process execution with blockchain technology.
While keeping the process execution off-chain, we developed an approach of inter-process communication using the Ethereum blockchain as a messaging channel.
Having a permanent ledger as the underlying data structure storing messages, faults and misunderstandings can be traced back to their origin and responsibilities are disclosed.
Building on the findings of this paper, improvements regarding runtime and execution costs open up a wide area of possible future work on the topic.
